---
title: "R4ds_2e_Exercise"
author: "Yash"
format: html
editor: visual
warning: false
---

## Exercise 2.4.3

```{r}
library(tidyverse)
library(palmerpenguins)
```

#### 1. Make a bar plot of `species` of `penguins`, where you assign `species` to the `y` aesthetic. How is this plot different?

```{r}
ggplot(data = penguins,
       mapping = aes(y = species ))+
  geom_bar()
```

#### 2. How are the following two plots different? Which aesthetic, `color` or `fill`, is more useful for changing the color of bars?

```         
ggplot(penguins, aes(x = species)) +
  geom_bar(color = "red")

ggplot(penguins, aes(x = species)) +
  geom_bar(fill = "red")
```

```{r}
ggplot(penguins, aes(x = species)) +
  geom_bar(color = "red") 
```

##### color argument only give colors to bar outline

```{r}
ggplot(penguins, aes(x = species)) +
  geom_bar(fill = "red")

```

##### fill argument fill the color inside the bars

#### 3. What does the `bins` argument in [`geom_histogram()`](https://ggplot2.tidyverse.org/reference/geom_histogram.html) do?

```{r}
ggplot(penguins, aes(x = body_mass_g)) +
  geom_histogram(bins = 20)
```

#### 4. Make a histogram of the `carat` variable in the `diamonds`dataset that is available when you load the tidyverse package. Experiment with different binwidths. What binwidth reveals the most interesting patterns?

```{r}
ggplot(diamonds, aes(x = carat)) +
  geom_histogram(binwidth = 0.10)

```

```{r}
ggplot(diamonds, aes(x = carat)) +
  geom_histogram(binwidth = 0.90)
```

```{r}
ggplot(diamonds, aes(x = carat))+
  geom_histogram(binwidth = 1)
```
